Application of the least-squares method to the multiscale transport equation in porous media

### 2011-05-09 MSTE_methodology.tex
with more physical meaning?

\newcommand{\TODO}[1]{\textcolor{blue}{TODO: #1} \\}
\newcommand{\Fede}[1]{\textcolor{green}{Fede: #1} \\}
\newcommand{\Pablo}[1]{#1}
\newcommand{\newf}[1]{#1}
\newcommand{\nof}[1]{\textcolor{cyan}{}}
%\newcommand{\nof}[1]{\textcolor{cyan}{{\sout{#1}}}}

@@

In the manufacturing solution method we propose a solution $\phi(\xi, z)$ and calculate analitically the value of the source. For this problem the chosen values are:

@@

>>>>

\newcommand{\TODO}[1]{\textcolor{blue}{TODO: #1} \\}
\newcommand{\Fede}[1]{\textcolor{green}{Fede: #1} \\}
\newcommand{\rev}[1]{\textcolor{red}{#1} \\}
\newcommand{\Pablo}[1]{#1}
\newcommand{\newf}[1]{#1}
\newcommand{\nof}[1]{\textcolor{cyan}{}}
%\newcommand{\nof}[1]{\textcolor{cyan}{{\sout{#1}}}}

@@

In the manufacturing solution method we propose a solution $\phi(\xi, z)$ and calculate analitically the value of the source. For this problem the chosen functionalities and values are:

@@

\rev{The selected model was based on physical cases. The porosity expands for pore sizes going from 1 mm to 10 mm. Pore sizes might be extended to various order of magnitudes below one millimetre if the rock presents work or fractures. However, for a pack of solid bodies 1 mm can be a reasonable magnitude. The pore space is has a maximum at 5.5 mm, and a total porosity of 24\% (note that this is very close to the ideal close pack porosity of $\tfrac{\pi}{18}$). The discharge $q$ depends with the porosity and a factor that scales with the square of the pore size as in pipes. The redistribution discharge follow the model of symmetric mixing with length $L$}.
